---
title        : "Reproducible Research: Peer Assessment 1"
output       : html_document
keep_md      : true
author       : "Jacques Francky SALOMON"
date         : "Sunday, July 19, 2015"
---


## Loading and preprocessing the data
```{r loadfiles}
# Loading
   pathD<- "C:/Users/USEE/Google Drive/Fcy ji_Formation/Library/R/Coursera/6.- Reproducible Research/Ass 1/repdata-data-activity"
   name1<- "activity.csv"
   setwd(pathD)
   data<- read.csv2(name1, header=T, sep=",")

# Process/transform the data (if necessary)
  str(data)       # Get a look of the variables.

```


## What is mean total number of steps taken per day?
```{r part2}
# 1. Calculate the total number of steps taken per day
  (Suum<- tapply(data$steps, data$date, sum))

# 2. Make a histogram of the total number of steps taken each day
  hist(Suum)

# Calculate and report the mean and median of the total number of steps taken per day
  (Mean<-mean(Suum, na.rm=TRUE))
  (Median<-median(Suum, na.rm=TRUE))

```


## What is the average daily activity pattern?
```{r part3}
library(dplyr)
# 1 Make a time series plot
   AverageAcross<- c()
   Interval<- c()
   for (j in 1:288){
      val<- data[j,3]
      f<- filter(data, data$interval==val)
      a<- f[,1]
      AverageAcross[j]<- mean(a, na.rm=TRUE)
      Interval[j]<- val
   }
   B2<-as.data.frame(cbind(AverageAcross,Interval))   
   B2$Interval<-as.factor(B2$Interval)
   attach(B2); str(B2)
   plot(Interval, AverageAcross, type = "l")

# 2 Which 5-minute interval,...
   vale<- max(B2$AverageAcross)
   f<- filter(B2, B2$AverageAcross==vale)
   show(f)
```
The 835th interval contains, on average across all the days in the dataset, the maximum number of steps which is 206.16.



## Imputing missing values

```{r part4}
#  1. Calculate and report the total number of missing values in the dataset (i.e. the total number of rows with NAs).
  a<-is.na(data$steps)
  a2<-data[a==TRUE,]
  nrow(a2)
```
The number of rows with missing values is 2304.


### 2. Devise a strategy for filling in all of the missing values in the dataset.
I decide to replace the missing values by the mean/average of steps of the specified 5-minute-interval for the folowing reason:  
 - 1. the missing values are for all the day considering. So it's not possible to replace them by the mean of the day.
      And the steps can greatly be different considering the intrval.  
 - 2. We have already calulted the mean for by interval accross all days.

```{r}
### Create a new dataset that is equal to the original dataset but with the missing data filled in.
dataNew<- data
library(dplyr)
for (i in 1:nrow(dataNew)){
  if(is.na(dataNew[i,1])==TRUE){
    a2<-filter(B2, B2$Interval==dataNew[i,3])  # Replace the NA value by the mean 
    dataNew[i,1]<- a2[[1]]                     # of the interval.
  }
}

### Make a histogram of the total number of steps taken...
  Suum2<- tapply(dataNew$steps, dataNew$date, sum)
  hist(Suum2)

### Calculate and report the mean and median of the total number of steps taken per day
  (Mean<-mean(Suum2, na.rm=TRUE))
  (Median<-median(Suum2, na.rm=TRUE))
```

Do these values differ from the estimates from the first part of the assignment? What is the impact of imputing missing data on the estimates of the total daily number of steps?  
Answ.- The mean is the same, but the standarsd deviations are a little different. After imputing the missing values, the standard deviation equals the mean, wich is a good indecator fo the absence od missing values. The fact that the means are equal before and after the imputing might means that the imputing system is a good one, or there were not too many Nas in tha dataset.

## Are there differences in activity patterns between weekdays and weekends?
```{r part5}

```





